Followers Are Not Enough: A Multi-faceted Approach to Community Detection in Online Social Networks

### 2014-11-24 paper-postreview/conclusions.tex
random edit

%Start of future work**
Our findings may have important implications to a common problem in social network analysis: identification of influential individuals---but further work must be carried out.
\alert{maybe move the top 10 people here}
 Many network measures of influence are based on the various types of centrality (degree, betweenness, closeness, eigenvector, etc.)~\cite{newman2009networks}. Most centralities depend explicitly on the structure of the network under consideration. But we have seen in our study that the structural network only highlights one of many possible ways that users interact with online social media.
Thus, a na\"ive application of centrality measures to a structural network may be answering a different question than the one motivating influence detection. For example, a user exhibiting high closeness centrality based on the structural network may be able to make a message visible to most other users in a social network, but this does not mean that those other users are likely to respond to or propagate that message. The importance of correctly framing network measures of influence has been explored previously~\cite{kitsak2010identification}, and our work further highlights its importance.

>>>>

%Start of future work**
Our findings may have important implications to a common problem in social network analysis: identification of influential individuals---but further work must be carried out.
 Many network measures of influence are based on the various types of centrality (degree, betweenness, closeness, eigenvector, etc.)~\cite{newman2009networks}. Most centralities depend explicitly on the structure of the network under consideration. But we have seen in our study that the structural network only highlights one of many possible ways that users interact with online social media.
Thus, a na\"ive application of centrality measures to a structural network may be answering a different question than the one motivating influence detection. For example, a user exhibiting high closeness centrality based on the structural network may be able to make a message visible to most other users in a social network, but this does not mean that those other users are likely to respond to or propagate that message. The importance of correctly framing network measures of influence has been explored previously~\cite{kitsak2010identification}, and our work further highlights its importance.
